New cardinality estimation algorithms for HyperLogLog sketches

### 2016-08-21 paper/paper.tex
some minor changes, updated .gitignore

@@

>>>>

\label{equ:sufficient_joint_statistic}

@@

The inclusion-exclusion method does not use all the information given by the sufficient statistic \eqref{equ:sufficient_joint_statistic}, because the estimates are functions of the three vectors $(\boldsymbol\symCountVariate^{<}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{1})$, 
$(\boldsymbol\symCountVariate^{<}_{2} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{2})$, and 
$(\boldsymbol\symCountVariate^{>}_{1} + \boldsymbol\symCountVariate^{=} + \boldsymbol\symCountVariate^{>}_{2})$. In contrast, the maximum-likelihood method uses all values of the sufficient statistic \eqref{equ:sufficient_joint_statistic}.
